Understanding Urban Bicycle Theft: Identifying Key Predictors for Risk Assessment

### 2024-11-26 paper/paper.qmd
simulation of data

---
title: "Exploring Urban Patterns in Bicycle Theft: Identifying Key Predictors and Trends"
subtitle: "An Analysis of Bicycle Theft Patterns and Predictors in Toronto"
author: 
  - Tommy Fu
thanks: "Code and data are available at: https://github.com/YichengFu/bike_thefts_analysis.git."
date: today
date-format: long
toc: true
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Understanding Urban Bicycle Theft: Identifying Key Predictors for Risk Assessment"
subtitle: "An Analysis of Bicycle Theft Patterns and Predictors in Toronto"
author: 
  - Tommy Fu
thanks: "Code and data are available at: https://github.com/YichengFu/bike_thefts_analysis.git."
date: today
date-format: long
toc: true
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---
